### 2015-05-20 Harris_2015/models.Rmd
Add 3-species code
save model results better
add manuscript materials

  # Return the simulated values.
  # The rosalia function stores pairwise parameters in the upper
  # triangle of an n-by-n matrix and stores the species intercepts
  # along the diagonal, so these values are named accordingly.
  c(upper = b, diag = a)
}
```

@@

  # "True" interaction strengths, to save for later
  truth = par[1:choose(n_spp, 2)]

  # "True" intercepts, possibly adjusted below by environment
  alpha = par[-(1:choose(n_spp, 2))]

@@

  # Landscape starts as if betas were all zero
  x = matrix(
    plogis(rep(1, n_sites) %*% t(alpha) + env %*% alpha_env), 
    nrow = n_sites, 
    ncol = n_spp
  )

  # Gibbs sampling until enough iterations have passed *and* no species are totally absent
  while(incomplete & !give_up){
    i = i + 1
    for(j in 1:n_spp){
      x[,j] = rbinom(
        nrow(x),
        size = 1,
        prob = plogis(x %*% beta[ , j] + alpha[j] + env %*% alpha_env[,j])
      )
    }

@@

@@

```{r, cache=TRUE, eval = FALSE}
library("rosalia")

@@

  # Return the upper triangle of the interaction matrix,
  # which has all the beta values.
  relist(fit$par)$upper
}

@@

```{r, cache = TRUE}
fit_model = function(method_name, csv_names){
  fit = get(paste("fit", method_name, sep = "_"))
  out_list = lapply(
    csv_names, 
    function(x){
      file_info = as.integer(strsplit(x, "-|\\.csv")[[1]])

@@

      data.frame(
        n_spp = file_info[1], 
        n_loc = file_info[2],
        n_rep = file_info[3],
        truth = unlist(truth),
        predicted = fit(read.csv(full_path, row.names = 1)),
        method = method_name,
        stringsAsFactors = FALSE
      )
    }
  )
  do.call(rbind, out_list)
}
```

@@

@@

@@

results = do.call(
  rbind,
  lapply(
    list(cov_results, partial_results, pairs_results),
    function(x){
      residuals = residuals(
        lm(
          truth ~ predicted + 0, 
          data = x, 
          weights = 1/choose(n_spp, 2),
          y = TRUE
        )
      )
      cbind(x, residuals = residuals)
    }
  )
)

@@

@@

>>>>

  # Return the simulated values.
  # The rosalia function stores pairwise parameters in the upper
  # triangle of an n-by-n matrix and stores the species intercepts
  # along the diagonal, so these values are named accordingly.
  c(alpha  = a, beta = b)
}
```

@@

  # "True" interaction strengths, to save for later
  truth = par[1:n_spp]

  # "True" intercepts, possibly adjusted below by environment
  alpha = par[-(1:n_spp)]

@@

  # Landscape starts as if betas were all zero. Each species' occurrence probability
  # depends on its alpha value and on the environment (assuming alpha_env is not zero).
  x = matrix(
    plogis(rep(1, n_sites) %*% t(alpha) + env %*% alpha_env), 
    nrow = n_sites, 
    ncol = n_spp
  )

  # Gibbs sampling until enough iterations have passed *and* no species are totally absent
  while(incomplete & !give_up){
    i = i + 1

    # Each round of Gibbs sampling updates one species (column) across all sites
    # according to its conditional probability (i.e. conditional on environment
    # and the other species that are present).
    for(j in 1:n_spp){
      x[,j] = rbinom(
        nrow(x),
        size = 1,
        prob = plogis(x %*% beta[ , j] + alpha[j] + env %*% alpha_env[,j])
      )
    }

@@

You can use the code below on the same simulated landscapes that I used by unzipping
the `fakedata.zip` file included with this file.

@@

```{r, cache=TRUE}
library("rosalia")

@@

  # Return the upper triangle of the interaction matrix,
  # which has all the beta values.
  fit$beta[upper.tri(fit$beta)]
}

@@

```{r, cache = TRUE}
library(parallel)
fit_model = function(method_name, csv_names){
  fit = get(paste("fit", method_name, sep = "_"))
  out_list = mclapply(
    csv_names, 
    function(x){
      file_info = as.integer(strsplit(x, "-|\\.csv")[[1]])

@@

      data.frame(
        n_spp = file_info[1], 
        n_loc = file_info[2],
        n_rep = file_info[3],
        truth = unlist(truth),
        predicted = fit(as.matrix(read.csv(full_path, row.names = 1))),
        method = method_name,
        stringsAsFactors = FALSE
      )
    }
  )
  do.call(rbind, out_list)
}
```

@@

```{r, cache = TRUE}
rosalia_results = fit_model("rosalia", grep("^[^2]", dir("fakedata/matrices"), value = TRUE))
```

@@

```{r}
str(rosalia_results)
```

@@

results = do.call(
  rbind,
  lapply(
    list(
      rosalia_results, 
      cov_results, 
      partial_results, 
      pairs_results
    ),
    function(x){
      residuals = residuals(
        lm(
          truth ~ predicted + 0, 
          data = x, 
          weights = 1/choose(n_spp, 2),
          y = TRUE
        )
      )
      cbind(x, residuals = residuals)
    }
  )
)

@@

write.csv(summarized_results, "summarized_results.csv")

@@

How often does each method get the sign of the interaction correct?
```{r, cache = TRUE}
sapply(
  list(partial = partial_results, pairs = pairs_results, rosalia = rosalia_results, cov = cov_results), 
  function(x){
    signif(100 * mean(sign(x$predicted) == sign(x$truth)), 3)
  }
)
```

Compare with the percent correct one would obtain "by chance" if one knew that 75%
of the true interactions were negative
```{r, cache = TRUE}
signif(
   100 *mean(rbinom(10000, size = 1, prob = .75) == rbinom(10000, size = 1, prob = .75)),
  3
)
```
